Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-01 WSSSPE2_report/WSSSPE2_review.tex
Section 4: microscopic changes.
minor bib + other fixes

Lightning talks is a new feature in WSSSPE2. Every talk in it were given only 2
minutes.

@@

Third that we could change academic culture, rather than worrying about the
systems. This was mostly focused on citations, because they matter for hiring,
promotion, and tenure decisions. The group discussed how we could weigh the
citations within papers better than we now do? How could we identify the five
citations that really matter for a paper, distinguishing them from the related
works and general background that are also cited. Perhaps we could break these
out in the reference list, working with publishers to implement this. Or maybe
we could also break out categories of citations, such as the most important
software used, the previous publication that we are building from, the data that
we actually used, etc. The Moore Foundation's award in data science \choinote{cite} was given as
an example, asking proposers: What are the five canonical citations that are
most important to your work? This would be a way of giving credit and assigning
importance to these works, differently from how we just count citations today. A
possible action that the group discussed was conducting a longitudinal study of
most useful \{software, data, etc.\} in a discipline.

@@

After this discussion, group A brainstormed about incentives,
with the following items suggested:
\begin{itemize}
\item running programming contests, creating bounties for contributing to open
source software, etc.
\item augment author lists to give credit to people who don't now get credit
(and making them machine readable)
\item developing a microcitation standard and mechanism (for both software and
data)
\item developing a well-defined standard for author contribution -- what level
of contribution rises to the level of authorship?
\item leveraging social media for citation and reviewing of content -- then
using social media to bring more people into the review process than is
traditional
\item determining where else software can be cited and recorded (e.g.,
acknowledgments sections of papers)
\item developing a taxonomy of contributors, tied to places that these metrics
are already stored (e.g., ORCID) \choinote{cite}
\item making metadata easier to add for software, creating incentive for
providing software metadata -- note that this cannot be centralized
\item creating something like the h-index that tenure committees can make use of
- simplify a way of measuring and documenting the overall credit given to an
individual over different projects
\item thinking about publishing software versus journal - software does not have to
be novel
\item determining guidelines for recommending software characteristics for
tenure - perhaps draft guidelines then get ACM or IEEE agreement
\end{itemize}

@@

The following general points were initially discussed: 
\begin{itemize}
\item The FLASH \choinote{cite} project was suggested as an example of how something 
like this has been done.
\item This data could be a file that can be associated with a citation to the 
software, either through use of a DOI for the credit file, or by uploading the 
credit files as associated with the paper.
\item This idea could also be applied to data
\item This data (the credit file) should be part of the metadata that is outside
of paywalls, like citations are now.
\item It was suggested that there should also be a separate file to track
software dependencies, but this is not the same file. 
\end{itemize}

>>>>

Lightning talks is a new feature in WSSSPE2. Every talk in it were given only two
minutes.

@@

Third that we could change academic culture, rather than worrying about the
systems. This was mostly focused on citations, because they matter for hiring,
promotion, and tenure decisions. The group discussed how we could weigh the
citations within papers better than we now do? How could we identify the five
citations that really matter for a paper, distinguishing them from the related
works and general background that are also cited. Perhaps we could break these
out in the reference list, working with publishers to implement this. Or maybe
we could also break out categories of citations, such as the most important
software used, the previous publication that we are building from, the data that
we actually used, etc. The Moore Foundation's award in data science was given as
an example, asking proposers: What are the five canonical citations that are
most important to your work?~\cite{moore-canonical} This would be a way of giving credit and assigning
importance to these works, differently from how we just count citations today. A
possible action that the group discussed was conducting a longitudinal study of
most useful \{software, data, etc.\} in a discipline.

@@

After this discussion, group A brainstormed about incentives,
with the following items suggested:
\begin{itemize}
\item running programming contests, creating bounties for contributing to open
source software, etc.
\item augment author lists to give credit to people who don't now get credit
(and making them machine readable)
\item developing a microcitation standard and mechanism (for both software and
data)
\item developing a well-defined standard for author contribution -- what level
of contribution rises to the level of authorship?
\item leveraging social media for citation and reviewing of content -- then
using social media to bring more people into the review process than is
traditional
\item determining where else software can be cited and recorded (e.g.,
acknowledgments sections of papers)
\item developing a taxonomy of contributors (e.g., Project Credit~\cite{projectcredit}) tied to places that these metrics
are already stored (e.g., ORCID) \cite{orcid}
\item making metadata easier to add for software, creating incentive for
providing software metadata -- note that this cannot be centralized
\item creating something like the h-index that tenure committees can make use of
- simplify a way of measuring and documenting the overall credit given to an
individual over different projects
\item thinking about publishing software versus journal - software does not have to
be novel
\item determining guidelines for recommending software characteristics for
tenure - perhaps draft guidelines then get ACM or IEEE agreement
\end{itemize}

@@

The following general points were initially discussed: 
\begin{itemize}
\item The FLASH~\cite{flash} project was suggested as an example of how something 
like this has been done.
\item This data could be a file that can be associated with a citation to the 
software, either through use of a DOI for the credit file, or by uploading the 
credit files as associated with the paper.
\item This idea could also be applied to data
\item This data (the credit file) should be part of the metadata that is outside
of paywalls, like citations are now.
\item It was suggested that there should also be a separate file to track
software dependencies, but this is not the same file. 
\end{itemize}
